%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the .tex file. 
% The resume.cls file provides the resume style used for structuring the document.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%






%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in, top=0.6in, right=0.75in, bottom=0.6in]{geometry} % Document margins
\usepackage[colorlinks=true, citecolor=blue]{hyperref} % Hypertext links in the document
% citecolor (green): Color for bibliographical citations in text.
\usepackage{tabu}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}




\name{Liang Fu} % Your name
\address{\small Last updated: Feb. 2021}
%\address{Hudson Building - Room 103} % Your address
%\address{1400 Washington Avenue, Albany, NY 12222} % Your secondary address (optional)
%\address{\href{mailto:lfu@albany.edu}{lfu@albany.edu} \\ (+1) 518-423-8555} %  Your phone number and your email






\begin{document}
	
%----------------------------------------------------------------------------------------
%	Contact Information
%----------------------------------------------------------------------------------------
\begin{tabu} to \linewidth {X[l]X[r]}
	%	 & \emph{Office:} (212) 998-8036 \\
	Hudson Building, Room 103     &  \href{mailto:lfu@albany.edu}{lfu@albany.edu}  \\
	1400 Washington Avenue        & +1 (518) 423-8555\\
	Albany, NY 12222              &  \href{http://liangfu.weebly.com}{http://liangfu.weebly.com}
\end{tabu}
\bigskip \bigskip




%----------------------------------------------------------------------------------------
%	Contact Information
%----------------------------------------------------------------------------------------
%\begin{rSection}{Contact Information}
%{\bf Email:} \href{mailto:lfu@albany.edu}{lfu@albany.edu}   \\
%{\bf Phone:} (+1) 518-423-8555  \\
%{\bf Office Address:} Hudson Building - Room 103, 1400 Washington Avenue, Albany, NY 12222 \\
%{\bf Home Address:} 101 Lincoln Avenue, Albany, NY 12206
%\end{rSection}
%\bigskip \bigskip





%----------------------------------------------------------------------------------------
%	Education 
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
%--copy and paste this region  if you need more--
Ph.D. Economics, {\bf University at Albany, SUNY}                     
  \begin{itemize}
  	\item[] \underline{Thesis Title}: Essays on international economics 
  	\item[] \underline{Expected Completion Date}: August 2021
  \end{itemize}
M.A. Economics, {\bf Central University of Finance and Economics}    \hfill {\em 2014} \\
B.S. Management, {\bf Qingdao University}                            \hfill {\em 2011} \\
\end{rSection}
\bigskip \bigskip






%----------------------------------------------------------------------------------------
%	Teaching and Research Fields
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching and Research Fields}
{\bf Primary fields:} Monetary Economics, International Economics \\ 
{\bf Secondary fields:} Chinese Economy  \\
\end{rSection}
\bigskip \bigskip






%--------------------------------------------------------------------------------
%    Research Papers
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Research Papers}
``Political Stability and Credibility of Currency Boards'' (with Shu Feng, Chun-Yu Ho and Wai-Yip Alex Ho) [\underline{Submitted}] \\
Abstract: This paper examines the credibility of currency boards of Argentina, Bulgaria, Estonia, Hong Kong, Latvia and Lithuania. We employ a Markov switching model to estimate the credibility of a currency board with the expected rate of depreciation induced by self-fulfilling behavior. The currency board of our sample countries are all subject to self-fulfilling behavior, which suggests that the credibility of a currency board determines the expected rate of depreciation. We also find evidences that the credibility of currency boards positively relates to the political stability of adopting economies.
\\
\\
``Real Exchange Rate and Innovation: Firm-Level Evidence from China'' (with Chun-Yu Ho and Xiaoli Zhang) \\
Abstract: This paper examines how exchange rate movement affects firms' innovation activities using a panel dataset of Chinese manufacturing firms. We construct firm-specific effective real exchange rate (RER) to measure the exchange rate shocks faced by each firm according to its composition of trading partners.  Our empirical results report that a 10\% increase in effective RER (i.e. depreciation) increase the share of new product sales in total sales by about 0.2 percentage points. Our result is robust to 1) the inclusion of firm- and industry-specific control variables, firm-specific fixed effects and year effects; and 2) the use of alternative weighting in constructing effective RER and alternative estimation methods. Nonetheless, there is no evidence showing that firm-specific RER shocks affect patent application, which suggests that the quality of innovation brought by RER fluctuations is limited. We further show that a better export opportunity is the main channel through which a depreciation of exchange rate promotes innovation activities. A better export opportunity leads to a higher revenue from export, which in turn, we argue that, relaxes the financial constraint faced by firms to conduct innovation activities.
\\
\\
``Differential Regional Effects of U.S. Monetary Policy'' \\
Abstract: This paper finds that U.S. monetary policy had different effects across different states during the 1979-2007 period by estimating a near vector autoregressive (VAR) model, in which each state's economy is affected by the national monetary policy as well as regional variables, while the common monetary policy responds only to aggregate macroeconomic variables. We show that states in which (durable) manufacturing accounts for a larger share of gross state product tend to be more sensitive to monetary policy shocks, which is consistent with previous studies using region-level data. States containing a larger concentration of small firms are more responsive to
monetary policy innovations, providing evidence for a broad credit channel.
\\

\end{rSection}
\bigskip \bigskip




%--------------------------------------------------------------------------------
%    Research Papers in Progress
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Research Papers in Progress}
``The Response of Financial Markets to Monetary Policy: Evidence from China''\\
Abstract: This paper identifies monetary policy actions and statements that signal changes in the monetary policy
stance and examine the response of financial markets to these signals. In particular, we construct unanticipated components of announced monetary policy changes.
\\
\\``The Impact of China's Monetary Policy on Exchange Rates: A Study using High-frequency Data''\\
Abstract: This paper examines the behavior of the Chinese renminbi/U.S. dollar exchange rate in reaction to China's monetary policy announcements, using an event study approach coupled with intra-day high-frequency data.
\\
\\
``The Impact of Elderly Care on Migration Decisions of Rural Residents in China''
\\
Abstract: Since the household registration (hukou) system in China prevents rural citizens from enjoying the welfare benefits provided by urban areas, the rural migrant workers have to leave their parents behind in the villages. Due to lack of social care in rural China, adult children have to take care of their parents when they’re old or physically disadvantaged. This paper tests the hypothesis that provision of elderly care would reduce rural residents' participation in migrant labor markets using the survey data from China Health and Retirement Longitudinal Study (CHARLS). 
	

\end{rSection}
\bigskip \bigskip





%----------------------------------------------------------------------------------------
%    Teaching Experience
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching Experience}
{\bf Instructor}{, University at Albany, SNUY} \hfill {\em 08/2018 - current}
 \begin{itemize}
     \item[] AECO 350 Money and Banking (Summer 2018, Fall 2018, Fall 2019, Spring 2020) 
     \item[] AECO 301 Intermediate Macroeconomics (Spring 2019, Fall 2020, Spring 2021)
 \end{itemize} 
{\bf Teaching Assistant}{, University at Albany, SUNY} \hfill {\em 09/2014 - 05/2016}
   \begin{itemize}
     \item[] AECO 700 Microeconomics II (Spring 2016)
     \item[] AECO 455 Public Microeconomics (Spring 2016)
     \item[] AECO 420 Applied Econometrics (Fall 2015)
     \item[] AECO 370 Economics of Labor (Fall 2014, Spring 2015) 
   \end{itemize} 
\end{rSection}
\bigskip \bigskip





%----------------------------------------------------------------------------------------
%	Working Experience
%----------------------------------------------------------------------------------------
\begin{rSection}{Working Experience}
	{\bf Research Assistant}{, New York State Division of the Budget} \hfill {\em 05/2016 - 08/2018}
\end{rSection}
\bigskip \bigskip






%--------------------------------------------------------------------------------
%   Honors and Awards 
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Honors and Awards} 
{\bf Helen Horowitz Excellence in Teaching Award}{, University at Albany, SUNY} \hfill{\em 2019}  \\ 
{\bf Distinction in Preliminary Examinations}{, University at Albany, SUNY} \hfill{\em 2015}  \\
\end{rSection}
\bigskip \bigskip





%----------------------------------------------------------------------------------------
%	Skilss
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills and Certificates}
{\bf Computer:} R, MATLAB, Python, Stata, SAS, LATEX
\\
{\bf Finance:} Passed CFA Level I
\\
{\bf Language:} Chinese Mandarin (Native), English (Fluent) 
\end{rSection}
\bigskip \bigskip








%----------------------------------------------------------------------------------------
%	Personal Information
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Information }
%--copy and paste this region  if you need more--
{\bf Date of Birth:} July 7, 1989  \\
{\bf Gender:} Male  \\
{\bf Citizenship:} China
\\
\end{rSection}




\end{document}----------------------------

